---
title: "Alcohol vs Seat choice"
author: "Sierra Green"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The Back row drinks 8 1/2 a week, the front row drinks 1 3/4 a week, and lastly the middle row drinks 3.3 a week whereas the back row drinks more than the rest. It seems that there are not drinking the same amount.


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value represents the chances of getting a result like we just obtained if the null hypothesis is actually true. Since the result is so small, I reject the null hypothesis.
We need to try and discover what is different from the other.
```{r}
plot(TukeyHSD(model1))
```

Based on the chart, the front and the middle are no different from another. The front/back and the back/middle are in fact different from each other.


## Conclusions


